---
title: "ESM262 Assignment 1"
author: "Anna Abelman and Bobby Miyashiro"
date: "2/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r}
logistic_growth <- function(r, N, K) {
  N = ifelse((N < 0), return("N cannot be less than 0"), N)
  K = ifelse((K <=0), return ("K cannot be less than 0"), K)
  dN_dt = r*N*(1-(N/K))
  return(dN_dt)
}
```

### Part I: Create a data frame

```{r}
#create normal distribution and make into data frame
nsample = 100
N = rnorm(mean = 50,sd = 10, n = nsample)

growth_df <- data.frame(population = N, dN_dt = NA)

#use logistic_growth function to determine the dN/dt
growth_df$dN_dt = logistic_growth(r = 5, N, K = 100)

#graph it
ggplot(data = growth_df, aes(x = N, y = dN_dt))+
  geom_point()+
  theme_classic() +
  labs(title = "Population Growth Rate Over Time In Relation to Population Size")
```

**Figure 1.** Change in population over change in time in relation to population size.

Our function was based off of the logistic growth equation, dN/dt = rN(1-(N/K)), which shows population change over time with a known carrying capacity. This graph shows that as population size increases, population growth rate over time also increases up until a population size of 50. After a population size of 50, the population growth rate over time decreases until it reaches the carrying capacity of 100.

### Part II: Create another data frame

```{r}
#create dataframe using sequence
growth_df2 <- data.frame(r = seq(from = 1, to = 200), dN_dt = NA)

#find dN/dt using the function we created
growth_df2$dN_dt = logistic_growth(growth_df2$r, N = 50, K = 200)

#plot it
ggplot(data = growth_df2, aes(x = r, y = dN_dt))+
  geom_point()+
  theme_classic() +
  labs(title = "Population Growth Rate Over Time In Relation to Growth Rate")
```

**Figure 2.** Change in population over change in time in relation to growth rate.

Our function was based off of the logistic growth equation, dN/dt = rN(1-(N/K)), which shows population change over time with a known carrying capacity. This graph shows that as growth rate increases, population growth rate over time also increases. The relationship shown increases linearly.














